---
title: Posit Environment Installation Checklist
format: 
  PositQuarto-pdf:
    output-file: "Posit_Customer_Checklist.pdf"
params:
  wb_servers: 1
  connect_servers: 1
  pm_servers: 1
  os: "ubuntu22"
  auth: "saml"
---

```{r}
#| echo: false
customer_name <- "RStudio"

# Going to assume if server count >1 for a product its getting set up in the same cluster
user_provisioning<-"automatic"

install_date <- "2023-07-01"
csm <- "Shannon Hagerty (shannon@posit.co)"

```

**Installation Plan for:** `r customer_name`  
**Target Install Complete Date:** `r install_date` 

For any technical issues please fill out a support ticket following [these steps](https://support.posit.co/hc/en-us/articles/360004788294-How-do-I-submit-a-Support-ticket-). For all other questions please email your customer success rep `r csm`.

--- 

### Requirements for Installation:

-   `r params$wb_servers` server(s) for Posit Workbench

    -   [Minimum requirements](https://support.posit.co/hc/en-us/articles/115002344588-Configuration-and-sizing-recommendations)

    -   [What to know about your use case before sizing?](https://solutions.posit.co/admin-training/courses/workbench/07_scaling.html)

    -   [Sizing Calculator](https://gallery.shinyapps.io/instanceCalc/)

-   `r params$connect_servers` server(s) for Posit Connect

    -   [Minimum requirements](https://support.posit.co/hc/en-us/articles/115002344588-Configuration-and-sizing-recommendations)

    -   [What to know about your use case before sizing?](https://solutions.posit.co/admin-training/courses/connect/scaling.html)

-   `r params$pm_servers` server(s) for Package Manager

    -   [Minimum requirements](https://support.posit.co/hc/en-us/articles/115002344588-Configuration-and-sizing-recommendations)

```{r source_functions}
#| echo: false
#| output: false

library(tidyverse)
library(gt)
library(fs)

file_paths <- fs::dir_ls("R")
purrr::map(file_paths, function(path){source(path)})
```

### Installation Steps

```{r}
#| echo: false
#| warning: false
#| 
checklist_df <- get_checklist()


customer_conditions <- list_conditions(
  wb_servers = params$wb_servers,
  connect_servers = params$connect_servers,
  pm_servers = params$pm_servers,
  os = params$os,
  auth = params$auth
)

customer_checklist_df <- checklist_df |> 
  build_checklist(customer_conditions) |> 
  filter_table()


format_table(customer_checklist_df)

```


