---
title: Posit Environment Installation Checklist
format: PositQuarto-pdf
---

```{r}
#| echo: false
customer_name <- "RStudio"

# Going to assume if server count >1 for a product its getting set up in the same cluster
workbench_servers <- 2 
connect_servers <- 0
pm_servers<- 0

os <- "rhel"
auth <- "saml"
user_provisioning<-"automatic"

install_date <- "2023-07-01"
csm <- "Shannon Hagerty (shannon@posit.co)"

```

**Installation Plan for:** `r customer_name`  
**Target Install Complete Date:** `r install_date` 

For any technical issues please fill out a support ticket following [these steps](https://support.posit.co/hc/en-us/articles/360004788294-How-do-I-submit-a-Support-ticket-). For all other questions please email your customer success rep `r csm`.

--- 

### Requirements for Installation:

-   `r workbench_servers` server(s) for Posit Workbench

    -   [Minimum requirements](https://support.posit.co/hc/en-us/articles/115002344588-Configuration-and-sizing-recommendations)

    -   [What to know about your use case before sizing?](https://solutions.posit.co/admin-training/courses/workbench/07_scaling.html)

    -   [Sizing Calculator](https://gallery.shinyapps.io/instanceCalc/)

-   `r connect_servers` server(s) for Posit Connect

    -   [Minimum requirements](https://support.posit.co/hc/en-us/articles/115002344588-Configuration-and-sizing-recommendations)

    -   [What to know about your use case before sizing?](https://solutions.posit.co/admin-training/courses/connect/scaling.html)

-   `r pm_servers` server(s) for Package Manager

    -   [Minimum requirements](https://support.posit.co/hc/en-us/articles/115002344588-Configuration-and-sizing-recommendations)

```{r}
#| echo: false
#| output: false

library(tidyverse)
library(gt)
```
### Installation Steps

```{r}
#| echo: false
#| warning: false
#| 
checklist <- read_csv("install_checklist.csv")

checklist<-checklist |> 
  mutate(Info =case_when(is.na(Description)&is.na(Resources) ~ paste(""),
                         is.na(Resources) ~ paste(Description),
                         is.na(Description) ~ paste("<b>Resources: </b>",Resources),
                         TRUE ~ paste(Description,"<b>Resources: </b>",Resources))) 



checklist %>%
select(Category, Step, Info) %>%
group_by(Category)  %>%
gt() %>%
fmt_markdown(columns=Info) %>%
tab_style(style = list(cell_text(weight="bold", align="center")),
          locations = cells_row_groups()) %>%
tab_options(column_labels.hidden = TRUE,
              stub.border.width = px(2),
  stub.border.color = "black")


```


